---
title: "Rent Affordability"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    navbar:
    - { icon: "fa-linkedin", href: "https://www.linkedin.com/in/durand-sinclair/",align: right}
    - { icon: "fa-facebook", href: "https://www.facebook.com/durand.sinclair",align: right}
    source_code: embed
    #logo: ./data/CIC_Logo.png #Needs to be exactly the right size to fit in bar
    #theme: lumen
runtime: shiny
---

```{r global, include=FALSE}
# 0) PREPARE ENVIRONMENT -----------------------------
    setwd("/Users/durandsinclair/datascience/govhack2018/explore/durand")

    #Load libraries
    library(flexdashboard)
    library(spdplyr)
    library(dplyr)
    library(readr)
    library(stringr)
    library(highcharter)
    library(leaflet)
    library(DT)
    library(here)
    library(geojsonio)
    library(geojsonlint)

#1) GET DATA ---------------------------
    #jobs <- read_csv(here("data", "income_by_jobs.csv"))
    cities <- read_csv(here("data", "city_coordinates.csv"))
    oz_merged <- readRDS(here("data", "consolidated", "oz_merged.rds"))
    

#2) SET UP LEAFLET ----------------------------------------------
    leaflet(options = leafletOptions(minZoom = 0, maxZoom = 18))
```


Income
=======================================================================

Row {row-height= 50}
-----------------------------------------------------------------------

### Your income p.a.

```{r}
renderValueBox({
    #Income box
    valueBox(
        prettyNum( paste( "$", round(input$income/1000, 0), " k"), big.mark = ","),
        icon = "fa-user"
        )
})
```

### Maximum Rent p.a.
```{r}
renderValueBox({
    #Maximum rent box
    valueBox(
        prettyNum( paste("$", round(input$income * 0.3 / 1000, 0), "k"), big.mark = ",")
        , icon = "fa-home"
        ) 
})
```

### Maximum Rent per week
```{r}
renderValueBox({
    #Maximum rent box
    valueBox(
        prettyNum( paste("$", round(input$income * 0.3 / 52, 0)), big.mark = ",")
        , icon = "fa-calendar"
        ) 
})
```


Row 
-----------------------------------------------------------------------
### Options {data-width=250}
```{r}

#List the cities, and allow the user to choose them from a drop down (selectInput)
    all_cities <- cities$gcc_names 

    #all_jobs <- job_summary 
        
    #All jobs
    #selectInput("job",
    #            label = "Pick a job: ", 
    #            choices = all_jobs,
    #            selected = "",
    #            selectize = FALSE
    #            )

    selectInput("city",
                label = "Choose a city: ",
                choices = all_cities,
                selected = "Greater Sydney",
                selectize = FALSE
                )
    numericInput(inputId = "income"
                 , label = "Household income"
                 , value = 100000
                 , min = 0
                 , max = 1000000
                 )

```


### Income Map
Breakdown of SA4s and their status based on the number of school aged children compared to the number of student places in local schools.
```{r}
renderLeaflet({
    
    #Categorise SA2s by rent stress
        this_city <- oz_merged %>%
            filter(GCC_NAME16 == input$city)

        good <- this_city %>%
            filter(rent <= input$income * 0.25)
        
        small_problem <- this_city %>%
            filter(rent > input$income * 0.25) %>%
            filter(rent <= input$income * 0.30)
        
        big_problem <- this_city %>%
            filter(rent > input$income * 0.3) %>%
            filter(rent <= input$income * 0.35)
        
        no_way <- this_city %>%
            filter(rent > input$income * 0.35)
    
        
    #Define areas using geojson
        #the_city <- geojson_json(this_city)
        good <- geojson_json(good)
        small_problem <- geojson_json(small_problem)
        big_problem <- geojson_json(big_problem)
        no_way <- geojson_json(no_way)
        
    #Produce map
        leaflet() %>% 
            addTiles() %>%
            addGeoJSON(geojson = good,
                       fillColor = "white",
                       weight = 1,
                       fill = TRUE,
                       fillOpacity = 0.2,
                       color = "purple"
                       ) %>%
            addGeoJSON(geojson = small_problem, 
                       fillColor = "orange", 
                       weight = 1, 
                       fillOpacity = 0.2, 
                       fill = TRUE, 
                       color = "purple"
            ) %>%
            addGeoJSON(geojson = big_problem, 
                       fillColor = "red", 
                       weight = 1, 
                       fillOpacity = 0.4, 
                       fill = TRUE, 
                       color = "purple"
            ) %>%
            addGeoJSON(geojson = no_way, 
                       fillColor = "black", 
                       weight = 1, 
                       fillOpacity = 0.7, 
                       fill = TRUE, 
                       color = "green"
            ) %>%
            addLegend("bottomright", 
                      color = c("orange", "red", "black"), 
                      labels = c("mild stress", "big stress", "no way"), 
                      title = "legend", 
                      opacity = 0.5
                      ) %>%
            setView(
                lat = cities %>% filter(gcc_names == input$city) %>% select(lat)
                , lng = cities %>% filter(gcc_names == input$city) %>% select(lon)
                , zoom = 8)


})
```


Model {.Storyboard}
================================================================================

### There was a high degree of correlation between ...

```{r}
```

### Fitted a model to predict how many hospitals should be in a county
```{r}

```

***
The results of the model were

- Residual standard error: [Number] on [df] degrees of freedom

- Multiple R Squared:  number

- Adjusted ***R-squared:  ***

- F-statistic:  274.1 on 3 and 572 DF

- ***p-value: < 2.2e-16***

And the formula was: 

- lm(formula = student_count ~ AREASQKM16 + children + school_count, 
    data = nsw_data)



